% Appendix C: Project logbook
% Per-member time logs.

\subsection*{Gijs Bomert}
\begin{longtable}{@{}p{2cm}p{9.5cm}p{2.5cm}@{}}
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endfirsthead
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endhead
\bottomrule
\endfoot
05-06 & Looking up sources and recording background knowledge. Setting up work OneDrive and collaboration ArcGIS project. Created EndNote source library. & 4h \\
07-06 & Looking up sources and starting a working draft of the introduction and discussion. & 5h \\
08-06 & Troubleshooting ArcGIS, resolving problems with EndNote integration into Word; reading further literature. & 3h \\
09-06 & Annotating sources, writing draft introduction and restructuring report. Cleaned the work OneDrive. & 5h \\
10-06 & Looking up datasets and supporting literature for land use regulation in Hawai\okina i. Implementing datasets in ArcGIS and exploring utilization. Set up working model for transforming data. Attended meeting reaffirming responsibilities. & 8h \\
11-06 & Filled in DAM tables, restructured model to implement new findings. Cataloguing ArcGIS tools required for new model. Building DAM flowchart. Discussed difficulties around transforming data and looked for solutions. & 9h \\
\end{longtable}

\subsection*{Max Claessens}
\begin{longtable}{@{}p{2cm}p{9.5cm}p{2.5cm}@{}}
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endfirsthead
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endhead
\bottomrule
\endfoot
05-06 & Locating data on elevation and getting familiar with it. & 1.5h \\
10-06 & Creating the DAM and the map for elevation. & 5h \\
11-06 & Finalizing the DAM. & 1h \\
16-06 & Meeting with supervisor and group meeting. & 30 min + 30 min \\
18-06 & Implementing feedback and assisting group where needed. & 5h \\
19-06 & Recording elevation part of presentation. & 15 min \\
20-06 & Making changes to maps for elevation and roads. & 1h \\
22-06 & Working on the suitability modeler. & 2.5h \\
23-06 & Final report work (intermediate maps and text). & 5h \\
\end{longtable}

\subsection*{Pieterjan Pauwelyn}
\begin{longtable}{@{}p{2cm}p{9.5cm}p{2.5cm}@{}}
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endfirsthead
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endhead
\bottomrule
\endfoot
04-06 & Discussion, preparation, brainstorming. & 2h \\
06-06 & Research suitability modeler and organisation. & 1h \\
09-06 & Drafting DAM section (precipitation and temperature). & 2h \\
15-06 & Refining DAM and flowchart. & 2h \\
16-06 & Feedback review and brainstorming. & 2h \\
18-06 & Building climate sub-models (four total). & 5h \\
19-06 & Presentation preparation and recording. & 2h \\
20-06 & Planning, reading, report work. & 1h \\
21-06 & Polishing and finishing sub-model maps. & 2h \\
22-06 & Methods section, figure descriptions. & 3--4h \\
23-06 & Final touches, re-mapping, formatting. & 2h \\
\end{longtable}

\subsection*{Ella Jansma}
\begin{longtable}{@{}p{2cm}p{9.5cm}p{2.5cm}@{}}
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endfirsthead
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endhead
\bottomrule
\endfoot
09-06 & Road DAM and layer creation (not finished fully). & 4.5h \\
10-06 & Working on the road map and organising next steps. & 2.5h \\
10-06 & Meeting to discuss the project. & 30 min \\
10-06 & Start the DAM flowchart and finish up the other parts. & 30 min \\
11-06 & Completing and formatting the DAM flowchart and table. & 1.5h \\
17-06 & Preparation meeting with supervisor, meeting and post-meeting discussion on how to proceed. & 3h \\
18-06 & Implement feedback from supervisor. & 2.5h \\
18-06 & Creating PowerPoint for presentations, creating task divisions, finishing up work needed for the presentation and writing text. & 3h \\
19-06 & Recording presentation part (and editing text). & 30 min \\
19-06 & Creating a video of all the separate presentation clips to get one output. & 1h \\
20-06 & Writing introduction (and finding literature). & 1.5h \\
21-06 & Writing introduction (and finding literature). & 3h \\
23-06 & Finishing introduction. & 3.5h \\
\end{longtable}

\subsection*{Jochem Oude Groeniger}
\begin{longtable}{@{}p{2cm}p{9.5cm}p{2.5cm}@{}}
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endfirsthead
\toprule
\textbf{Date} & \textbf{Task} & \textbf{Time devoted} \\
\midrule
\endhead
\bottomrule
\endfoot
05-06 & Orienting and starting on the soil layer. & 2.5h \\
10-06 & Working on layers and DAM, plus meeting. & 3h \\
11-06 & Working on DAM. & 2.5h \\
16-06 & Meeting and discussion. & 3h \\
17-06 & Incorporating feedback and starting on final model. & 3h \\
18-06 & Finishing final model and presentation. & 3.5h \\
19-06 & Recording video part. & 0.5h \\
22-06 & Updating DAM and report. & 1.5h \\
\end{longtable}
